Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-03-16 paperDistance/paper.tex
slight change to notation

We would like to infer the true parallax $\varpi_{true}$ to a star using the measured noisy parallax $\varpi$ and $\sigma_{\varpi}$ from \gaia. \gaia\ gives us the likelihood of the parallax of a star, given some unknown true parallax and uncertainties, which we assume to be a Gaussian
\begin{equation}
p(\varpi \given \varpi_{true}, \sigma_{\varpi},I) = \mathcal{N}(\varpi \given \varpi_{true}, \sigma_{\varpi})
\label{eq:gaialike}
\end{equation}

@@

\begin{equation}
\begin{aligned}
\mathrm{true \, vector} \;\;\;\; &\vec{Y} = [10^{0.2\,M_{J,n} + 2}, C_n] \\
\mathrm{data \, vector} \;\;\;\; &\vec{y} = [\varpi\,10^{0.2J^c_n}, (J- K)^c_n] \;  n \in \mathrm{stars} \\
\mathrm{with \; absolute \; magnitude} \;\;\;\; &M^c_{J,n} = J_n + 5\log_{10}\varpi_n - Q_J\,E(B-V)_n \\
\mathrm{and \; color} \;\;\;\; &(J - K)^c_n = J_n - K_n - Q_{JK}\,E(B-V)_n \\
\mathrm{assumptions} \;\;\;\; &I = \left\{\left\{\sigma^2_{\varpi, n}\right\}, \left\{\sigma^2_{J,n}\right\}, \left\{\sigma^2_{K,n}\right\}, \mathrm{Dust \, Map}\right\}
\end{aligned}
\label{eq:data}
\end{equation}

>>>>

Given these assumptions, we would like to infer the true parallax $\varpi_{true}$ to a star using the measured noisy parallax $\varpi$ and $\sigma_{\varpi}$ from \gaia. \gaia\ gives us the likelihood of the parallax of a star, given some unknown true parallax and uncertainties, which we assume to be a Gaussian
\begin{equation}
p(\varpi \given \varpi_{true}, \sigma_{\varpi},I) = \mathcal{N}(\varpi \given \varpi_{true}, \sigma_{\varpi})
\label{eq:gaialike}
\end{equation}

@@

\begin{equation}
\begin{aligned}
\mathrm{true \, vector} \;\;\;\; &\vec{Y} = [10^{0.2\,M_{J,n} + 2}, C_n] \\
\mathrm{data \, vector} \;\;\;\; &\vec{y} = [\varpi_n\,10^{0.2J^c_n}, (J- K)^c_n] \;  n \in \mathrm{stars} \\
\mathrm{with \; apparent \; magnitude} \;\;\;\; &J^c_n = J_n - Q_J\,E(B-V)_n \\
\mathrm{and \; color} \;\;\;\; &(J - K)^c_n = J_n - K_n - Q_{JK}\,E(B-V)_n \\
\mathrm{assumptions} \;\;\;\; &I = \left\{\left\{\sigma^2_{\varpi, n}\right\}, \left\{\sigma^2_{J,n}\right\}, \left\{\sigma^2_{K,n}\right\}, \mathrm{Dust \, Map}\right\}
\end{aligned}
\label{eq:data}
\end{equation}
